Scalar on Function Regression \\ with Applications to Near-Infrared Spectroscopy

### 2022-01-15 Presentation/slides.tex
push tables

% packages
%\usepackage[hmargin=2cm, vmargin=2cm]{geometry}
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[english]{babel}
\usepackage{setspace}
%\usepackage{xcolor}
\usepackage{multicol}
\usepackage{float}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[font=small,skip=2pt]{caption}
\captionsetup[figure]{labelformat=empty}
\usepackage[
backend=biber,
style=authoryear-comp,
]{biblatex}

@@

	\begin{frame}{Simulation Results}

		\begin{itemize}

			\item {\color{green} add results here!}
		\end{itemize}
	\end{frame}

>>>>

% packages
%\usepackage[hmargin=2cm, vmargin=2cm]{geometry}
\usepackage{microtype}
\usepackage{adjustbox}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[english]{babel}
\usepackage{setspace}
%\usepackage{xcolor}
\usepackage{multicol}
\usepackage{float}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[font=small,skip=2pt]{caption}
\captionsetup[figure]{labelformat=empty}
\usepackage[
backend=biber,
style=authoryear-comp,
]{biblatex}

@@

	\begin{frame}{Recap: Trade Off between Bias and Variance}
		\begin{figure}\notag
			\includegraphics[width = \textwidth]{../Graphics/basis_expansions.pdf}
		\end{figure}
	\end{frame}

	\begin{frame}{Simulation Results - bspline}
		\begin{table}
		\centering
\resizebox*{\columnwidth}{6.5cm}{%
\begin{tabular}{lllllll}
\cline{2-6}
 & \textbf{f1\_e1\_spline}                 & \textbf{f1\_e2\_spline}                 & \textbf{f2\_e1\_spline}                   & \textbf{f2\_e2\_spline}                 & \textbf{n\_basis} &  \\ \cline{2-6}
 & 2.13178119016857                        & {\color[HTML]{FD6864} 71.7099603226115} & 0.608171495504618                         & 1.53453412563582                        & 4                 &  \\
 & 2.00756061672648                        & 71.9395214288329                        & 0.342736147598609                         & 1.29059813220677                        & 5                 &  \\
 & {\color[HTML]{FD6864} 1.99374215191544} & 72.2563479644725                        & 0.245623228181924                         & 1.20138156565603                        & 6                 &  \\
 & 2.03648199621352                        & 73.7857088138923                        & 0.279709073157873                         & 1.24948462939122                        & 7                 &  \\
 & 2.18614795862507                        & 79.0485254545422                        & 0.104397806306425                         & 1.145842683177                          & 8                 &  \\
 & 2.05113790304629                        & 74.1783834857012                        & 0.0355899940503619                        & {\color[HTML]{FD6864} 1.02172959116332} & 9                 &  \\
 & 2.10522981230773                        & 76.1883552769234                        & 0.029691294210754                         & 1.03929073546751                        & 10                &  \\
 & 2.1011969989178                         & 76.4030798206724                        & {\color[HTML]{FD6864} 0.0296057602994908} & 1.04246508005367                        & 11                &  \\
 & 2.38150697658292                        & 86.1706579685565                        & 0.0369986801764011                        & 1.18191116948046                        & 12                &  \\
 & 2.21136870222925                        & 80.6207607207599                        & 0.0363026864816967                        & 1.10242516644568                        & 13                &  \\
 & 2.44947712911835                        & 87.6976578759761                        & 0.0380185616636571                        & 1.21257716080672                        & 14                &  \\
 & 2.28870905624113                        & 83.4755186453129                        & 0.0315198808793299                        & 1.13630733462095                        & 15                &  \\
 & 2.5490614406393                         & 93.593040512565                         & 0.0351718970102256                        & 1.26520057279256                        & 16                &  \\
 & 2.55139454545527                        & 93.3074090320499                        & 0.0352440364348144                        & 1.26610962599564                        & 17                &  \\
 & 2.75160520792553                        & 100.556190093422                        & 0.0380316879790874                        & 1.3620304183365                         & 18                &  \\
 & 3.02429148497643                        & 109.987580398216                        & 0.0409879625688711                        & 1.4813467852555                         & 19                &  \\
 & 3.42548075922108                        & 122.395980857659                        & 0.0471595536208038                        & 1.68537882583396                        & 20                &  \\
 & 3.63355571510069                        & 132.077208928751                        & 0.0490939239286374                        & 1.7750377827367                         & 21                &  \\
 & 5.93680459997264                        & 209.128064205703                        & 0.0779161032701813                        & 2.86105576687348                        & 22                &  \\
 & 9.63325470698287                        & 339.676032195418                        & 0.126422677097386                         & 4.65363116820157                        & 23                &  \\
 & 15.2728939666428                        & 545.827184915647                        & 0.200212312881423                         & 7.22652606521015                        & 24                &  \\
 & 13.9781506322669                        & 495.957265678323                        & 0.184269309019229                         & 6.6968929082163                         & 25                & 
\end{tabular}%
}
\end{table}

	\begin{frame}{Simulation Results - bspline}
		\begin{table}
		\centering
\resizebox*{\columnwidth}{!}{%
\begin{tabular}{lllllll}
\cline{2-6}
 & \textbf{f1\_e1\_spline}                 & \textbf{f1\_e2\_spline}                 & \textbf{f2\_e1\_spline}                   & \textbf{f2\_e2\_spline}                 & \textbf{n\_basis} &  \\ \cline{2-6}
 & 2.02918344408687                       & {\color[HTML]{FD6864} 72.0085477229407} & 0.511999648510189                         & 1.47468049635309                         & 3                &  \\
 & {\color[HTML]{FD6864} 2.0220366421201} & 72.60172284215                          & 0.16157756089415                          & 1.13746697354709                         & 5                &  \\
 & 2.0354924731897                        & 73.1836346250812                        & 0.0293072016650537                        & {\color[HTML]{FD6864} 0.990682620987463} & 7                &  \\
 & 2.06199840536677                       & 73.9631412481736                        & {\color[HTML]{FD6864} 0.0290190767234641} & 0.999385186246351                        & 9                &  \\
 & 2.08808310984254                       & 75.0920660376146                        & 0.0290873388349217                        & 1.01393568534507                         & 11               &  \\
 & 2.09974789215127                       & 75.9422236701681                        & 0.0294100223429063                        & 1.02909474969485                         & 13               &  \\
 & 2.1086767501285                        & 76.7123085769457                        & 0.0298036585996321                        & 1.03713735705978                         & 15               &  \\
 & 2.13013296583489                       & 77.4907530428231                        & 0.0300236821233963                        & 1.03980406503428                         & 17               &  \\
 & 2.15348157839283                       & 78.3942553410957                        & 0.030307463717998                         & 1.0508902800978                          & 19               &  \\
 & 2.17750745519215                       & 79.2057575714294                        & 0.0306501467540424                        & 1.06172373892826                         & 21               &  \\
 & 2.20581113466118                       & 80.3800790338639                        & 0.0309985992677207                        & 1.07695651700849                         & 23               &  \\
 & 2.23717951397715                       & 81.5089652049561                        & 0.0314869147262958                        & 1.09052842774153                         & 25               & 
\end{tabular}%
}
\end{table}
	\end{frame}
